How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-07-14 paper.tex
more text, reference github templates

@@

@@

If you're interacting with fellow users in a support forum, don't mock
questioners who are less experienced than you --- a question may seem foolish to
you, but even an uninformed or ill-directed question is an opportunity for
teaching; one of our goals for this document is that it become a resource to
educate new users of expected norms without consuming developers' time and
mental bandwidth.

>>>>

Once you've determined you need help, the next obvious step is to ask for it.
How should you go about doing so? Email the developer? Post in a forum? Raise an
issue on GitHub? Asking the question in the right venue will greatly increase
your chances of getting a timely answer. Step 1 is to check the documentation:
look at the manual, check the README on the GitHub repository, check the
software website, etc --- most of the time, at least one of these sources will
say how they prefer to receive bug reports, feature requests, etc. Actually,
there's a step 0: make sure you're looking at the right piece of software. This
might seem obvious, but I've received multiple requests for help with software I
had nothing to do with; once it took 8 emails back and forth before I figured
this out (but more on that problem later).

Asking in the right place is particularly important if the software is complex
or has a large user community --- there may be separate forums for bug reports,
usage help, and feature request, and asking in the wrong place will make it
unlikely the right people will see your question. Moreover, the first impression
you'll make is that you're someone who can't be bothered to read the
instructions, which will make them less inclined to help you.

@@

GitHub issue templates \cite{github-templates}

@@

If you're interacting with fellow users in a support forum, don't mock
questioners who are less experienced than you --- a question may seem foolish to
you, but even an uninformed or ill-directed question is an opportunity for
teaching. That said, we understand that answering the same questions repeatedly
is frustrating and exhausting; one of our goals for this document is that it
become a resource to educate new users of expected norms without consuming
developers' time and mental bandwidth.
